Oak resilience to drought and land-use show how the ecological and geographical rear-edges do not necessarily meet today

### 2019-09-23 man/ecosystems/ms_ecosystems.Rmd
update ms

Resumir párrafos de Vilá-Cabrera (los que ha puesto RZ)

>>>>

The response of species to changing environments is likely to be determined largely by population responses at range margins [@Hampe2005]. Peripheral populations are usually considered more vulnerable compared with populations occurring at the center of a species’ range (*i.e.* centre-periphery hypotheses) [CITAS]. It has been assumed that rear-edge populations have a concordance between geographical and ecological marginality, with lower performance and thus higher risk of extinction than those populations at the core of the species’ range [@VilaCabrera2019; @Pironon2016]. Nonetheless, recent reviews found species- and population- specific responses highlight that this hypothesis not always fulfill [*e.g.* Sexton2009; Abeli2014]. In this respect, to fully understand changes in distribution and abundance of species as a consequence of global change we need to know in which environmental conditions geographical marginallity does not correspond with ecological marginallity [@VilaCabrera2019].
